---
title: "ASAI 2020 Results"
output: 
  html_notebook: 
    code_folding: none
    fig_height: 6
    fig_width: 14
    toc: yes
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(stringr)
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(readr)
library(ggdark)
```


```{r eval=FALSE, include=FALSE}
library(ggplot2)
library(dplyr)
resultperclass<-read_csv("../results/results_per_subclass_test_kk.csv")

dga_results_plot<-ggplot(resultperclass  %>% filter(grepl('Normal',label)) %>% mutate(label=gsub("Botnet\\.","",label))
                         ,aes(x=label,y=recall))+
  geom_point(aes(size=support,fill='skyblue'),color='black',shape = 21,alpha=0.5)+
  geom_point(size=1,color='blue',fill='blue',shape = 21)+
  ylab("True Positive Rate [TPR]")+
  ggtitle("")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_color_gradient2(low = "cyan", mid='blue',high = "red")+
   xlab(' Malware families' )+
   guides(colour=FALSE,size=FALSE)+
    scale_size_continuous(range = c(5,15))+
  theme(legend.position="bottom")
dga_results_plot

```



# Results for CTU13:
### LSTM Woodbridge + 256 batchs + Masking after 10 executions + maxlen from 10 to 1000 + first 4 symbols removed

```{r echo=FALSE, message=FALSE, warning=FALSE}
#setwd("results/")
files <- list.files(path = "../results/",pattern="results_test_ctu13-lstm_endgame-\\d+")

#str_replace(string = "results_test_ctu13-lstm_endgame-80-1.csv",pattern = ".*-([0-9]+)-[0-9]+.csv","\\1")

results_lstm <- lapply(files, function(x) 
                read_csv(paste("../results/",x,sep=""))   
                %>% add_column(maxlen=as.integer(str_replace(string = x ,pattern = ".*-([0-9]+)-[0-9]+.csv","\\1") ))
                )

results_lstm <-do.call(rbind,results_lstm)

results_lstm  %>% arrange(maxlen) %>% filter(metric %in%  c("Balanced Accuracy","F1","Precision","Sensitivity","Specificity")) %>%
  ggplot() +
   labs(title="CTU13 [Train,Test] LSTM Woodbridge [10 executions]",
        subtitle="Masking, 256 batch, first 4 symbols removed\nMaxlen from 10 to 1000 ")+
  geom_boxplot(aes(x=as.factor(maxlen),y=value,fill=as.factor(maxlen)),color='black')+
  xlab("maxlen")+
  theme_bw()+
  dark_theme_gray()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")+
  facet_wrap(~metric, scales = "free")
```

### RF + maxlen from 10 to 1000 + first 4 symbols removed

```{r echo=FALSE, message=FALSE, warning=FALSE}
#setwd("results/")
files <- list.files(path = "../results/",pattern="results_test_ctu13-rf-*")

#str_replace(string = "results_test_ctu13-lstm_endgame-80-1.csv",pattern = ".*-([0-9]+)-[0-9]+.csv","\\1")

results_rf <- lapply(files, function(x) 
                read_csv(paste("../results/",x,sep=""))   
                %>% add_column(maxlen=as.integer(str_replace(string = x ,pattern = ".*-([0-9]+)-[0-9]+.csv","\\1") ))
                )

results_rf <-do.call(rbind,results_rf)

results_rf  %>% arrange(maxlen) %>% filter(metric %in%  c("Balanced Accuracy","F1","Precision","Sensitivity","Specificity")) %>%
  ggplot() +
  ggtitle("RF")+
  geom_boxplot(aes(x=as.factor(maxlen),y=value,fill=as.factor(maxlen)),color='black')+
  xlab("maxlen")+
  theme_bw()+
  dark_theme_gray()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")+
  facet_wrap(~metric, scales = "free")
```

### LSTM vs RF

```{r echo=FALSE, fig.width=12, message=FALSE, warning=FALSE, paged.print=TRUE}
results<-rbind(results_lstm %>% add_column(model="lstm"),results_rf %>% add_column(model="rf"))
#results

results %>% filter(metric %in%  c("Balanced Accuracy","F1","Precision","Sensitivity","Specificity")) %>%
  ggplot() +
  ggtitle("RF vs LSTM")+
  geom_boxplot(aes(x=as.factor(model),y=value,fill=as.factor(model)),color='black')+
  xlab("maxlen")+
  theme_bw()+
  dark_theme_gray()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")+
  facet_grid(metric~maxlen, scales = "free")

```

### RF trained with random sequences of maxlen=10 

Dataset ctu13subs.csv: ctu13.csv filtering sequences >75 and extracting subsquences of lenght=10 with random start
```{r echo=FALSE, message=FALSE, warning=FALSE}
files <- list.files(path = "../results/",pattern="results_test_ctu13-rf-sub*")


results_rf <- lapply(files, function(x) 
                read_csv(paste("../results/",x,sep=""))   
                %>% add_column(maxlen=as.integer(str_replace(string = x ,pattern = ".*-([0-9]+)-[0-9]+.csv","\\1") ))
                )

results_rf <-do.call(rbind,results_rf)
#results_rf
```

### LSTM trained with random sequences of maxlen=10 

LSTM Woodbridge + 256 batchs + Masking after 10 executions + maxlen from 10 to 1000 + first 4 symbols removed
Dataset ctu13subs.csv: ctu13.csv ~625 sequences. Filtering sequences >75 and extracting subsquences of lenght=10 with random start

```{r echo=FALSE, message=FALSE, warning=FALSE}
files <- list.files(path = "../results/",pattern="results_test_ctu13-lstm_endgame-sub*")

#str_replace(string = "results_test_ctu13-lstm_endgame-80-1.csv",pattern = ".*-([0-9]+)-[0-9]+.csv","\\1")

results_lstm <- lapply(files, function(x) 
                read_csv(paste("../results/",x,sep=""))   
                %>% add_column(maxlen=as.integer(str_replace(string = x ,pattern = ".*-([0-9]+)-[0-9]+.csv","\\1") ))
                )

results_lstm <-do.call(rbind,results_lstm)
#results_lstm
```

### LSTM vs RF random subsquence maxlen=10 using dataset with sequences >75

```{r echo=FALSE, message=FALSE, warning=FALSE}
results<-rbind(results_lstm %>% add_column(model="lstm"),results_rf %>% add_column(model="rf"))


results %>% filter(metric %in%  c("Balanced Accuracy","F1","Precision","Sensitivity","Specificity")) %>%
  ggplot() +
  ggtitle("RF vs LSTM")+
  geom_boxplot(aes(x=as.factor(model),y=value,fill=as.factor(model)),color='black')+
  xlab("maxlen")+
  theme_bw()+
  dark_theme_gray()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")+
  facet_wrap(~metric, scales = "free")
```

### LSTM vs RF random subsquence maxlen=10,25,75 using full dataset 

```{r echo=FALSE, message=FALSE, warning=FALSE}
files <- list.files(path = "../results/",pattern="results_test_ctu13-lstm_endgame-subs-fulldataset-correct*")


results_lstm <- lapply(files, function(x) 
                read_csv(paste("../results/",x,sep=""))   
                %>% add_column(maxlen=as.integer(str_replace(string = x ,pattern = ".*-([0-9]+)-[0-9]+.csv","\\1") ))
                )

files <- list.files(path = "../results/",pattern="results_test_ctu13-rf-subs-fulldataset-correct*")


results_rf <- lapply(files, function(x) 
                read_csv(paste("../results/",x,sep=""))   
                %>% add_column(maxlen=as.integer(str_replace(string = x ,pattern = ".*-([0-9]+)-[0-9]+.csv","\\1") ))
                )

results_rf <-do.call(rbind,results_rf)
results_lstm <-do.call(rbind,results_lstm)

results<-rbind(results_lstm %>% add_column(model="lstm"),results_rf %>% add_column(model="rf"))


results %>% filter(metric %in%  c("Balanced Accuracy","F1","Precision","Sensitivity","Specificity")) %>%
  ggplot() +
  ggtitle("RF vs LSTM")+
  geom_boxplot(aes(x=as.factor(model),y=value,fill=as.factor(model)),color='darkgray')+
  xlab("maxlen")+
  theme_bw()+
  dark_theme_gray()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")+
  facet_grid(maxlen~metric)
```

------

# Results for CTU19:

### LSTM Woodbridge + 256 batchs + Masking after 10 executions + maxlen from 10 to 1000 + first 4 symbols removed

```{r echo=FALSE, message=FALSE, warning=FALSE}

#setwd("results/")
files <- list.files(path = "../results/",pattern="results_test_ctu19-lstm_endgame-\\d+")

str_replace(string = "../results_test_ctu13-lstm_endgame-80-1.csv",pattern = ".*-([0-9]+)-[0-9]+.csv","\\1")

results_lstm <- lapply(files, function(x) 
                read_csv(paste("../results/",x,sep=""))   
                %>% add_column(maxlen=as.integer(str_replace(string = x ,pattern = ".*-([0-9]+)-[0-9]+.csv","\\1") ))
                )

results_lstm <-do.call(rbind,results_lstm)

results_lstm  %>% arrange(maxlen) %>% filter(metric %in%  c("Balanced Accuracy","F1","Precision","Sensitivity","Specificity")) %>%
  ggplot() +
  labs(title="CTU19 [Train,Test] LSTM Woodbridge [10 executions]",
        subtitle="Masking, 256 batch, first 4 symbols removed\nMaxlen from 10 to 1000 ")+
  geom_boxplot(aes(x=as.factor(maxlen),y=value,fill=as.factor(maxlen)),color='darkgray')+
  xlab("maxlen")+
  theme_bw()+
  dark_theme_gray()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")+
  facet_wrap(~metric, scales = "free")
```

### RF + maxlen from 10 to 1000 + first 4 symbols removed
```{r echo=FALSE, message=FALSE, warning=FALSE}
#setwd("results/")
files <- list.files(path = "../results/",pattern="results_test_ctu19-rf-\\d+")

#str_replace(string = "results_test_ctu13-lstm_endgame-80-1.csv",pattern = ".*-([0-9]+)-[0-9]+.csv","\\1")

results_rf <- lapply(files, function(x) 
                read_csv(paste("../results/",x,sep=""))   
                %>% add_column(maxlen=as.integer(str_replace(string = x ,pattern = ".*-([0-9]+)-[0-9]+.csv","\\1") ))
                )

results_rf <-do.call(rbind,results_rf)

results_rf  %>% arrange(maxlen) %>% filter(metric %in%  c("Balanced Accuracy","F1","Precision","Sensitivity","Specificity")) %>% #group_by(maxlen,metric) %>% summarise(mean=mean(value),sd=sd(value)) %>%
  ggplot() +
   labs(title="CTU19 [Train,Test] RF [10 executions]",
        subtitle="First 4 symbols removed\nMaxlen from 10 to 1000 ")+
  #geom_col(aes(x=as.factor(maxlen),y=mean,fill=as.factor(maxlen)),color='darkgray')+
   geom_boxplot(aes(x=as.factor(maxlen),y=value,fill=as.factor(maxlen)),color='darkgray')+

   xlab("maxlen")+
  dark_theme_gray()+

  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")+
  facet_wrap(~metric, scales = 'free')
```



### catboost + maxlen from 10 to 1000 + first 4 symbols removed
```{r echo=FALSE, message=FALSE, warning=FALSE}
#setwd("results/")
files <- list.files(path = "../results/",pattern="results_test_catboost_ctu19-\\d+")

#str_replace(string = "results_test_ctu13-lstm_endgame-80-1.csv",pattern = ".*-([0-9]+)-[0-9]+.csv","\\1")

results_catboost <- lapply(files, function(x) 
                read_csv(paste("../results/",x,sep=""))   
                %>% add_column(maxlen=as.integer(str_replace(string = x ,pattern = ".*-([0-9]+)-[0-9]+.csv","\\1") ))
                )

results_catboost <-do.call(rbind,results_catboost)

results_catboost  %>% arrange(maxlen) %>% filter(metric %in%  c("Balanced Accuracy","F1","Precision","Sensitivity","Specificity")) %>% #group_by(maxlen,metric) %>% summarise(mean=mean(value),sd=sd(value)) %>%
  ggplot() +
   labs(title="CTU19 [Train,Test] catboost [10 executions]",
        subtitle="First 4 symbols removed\nMaxlen from 10 to 1000 ")+
  #geom_col(aes(x=as.factor(maxlen),y=mean,fill=as.factor(maxlen)),color='darkgray')+
   geom_boxplot(aes(x=as.factor(maxlen),y=value,fill=as.factor(maxlen)),color='darkgray')+

   xlab("maxlen")+
  dark_theme_gray()+

  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")+
  facet_wrap(~metric, scales = 'free')
```


### LSTM vs RF

```{r echo=FALSE, fig.width=12, message=FALSE, warning=FALSE, paged.print=TRUE}
results<-rbind(results_lstm %>% add_column(model="lstm"),
               results_rf %>% add_column(model="rf"),
               results_catboost %>% add_column(model="catboost")
               
               )
#results

results %>% filter(metric %in%  c("Balanced Accuracy","F1","Precision","Sensitivity","Specificity")) %>%
  ggplot() +
  labs(title="CTU19 [Train,Test] RF vs LSTM vs catboost [10 executions]",
        subtitle="First 4 symbols removed\nMaxlen from 10 to 1000 ")+
  geom_boxplot(aes(x=as.factor(model),y=value,fill=as.factor(model)),color='darkgray')+
  xlab("maxlen")+
  theme_bw()+
  dark_theme_gray()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position="none")+
  facet_grid(metric~maxlen, scales = "free")

```
